---
title: "Map Visualization for commodities Imported or Exported among States in American "

output: html_document
---



### 1. The map shows the total value of each commodity exported from each state for Fuel oils,Gasoline,Meat/seafood three commodities.
````{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('map1.html')
```
````

For fuel oils, the state of Texas has the largest export values 135600 million dollars among continous states and DC.
For gasoline, the state of Texas has the largest export values 154700 million dollars among continous states and DC.
For meat/seafood, the state of California has the largest export values 32300 million dollars among continous states and DC.


### 2. The map shows the largest imported commodity into each state in terms of tonnage.
````{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('map2.html')
```
````
The map shows the state of texas has the largest imported commodities in terms of tonnage, the commodity is gasoline


### 3. The map shows the flow of meat/seafood into the state of Virginia by truck.
````{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('map3.html')
```
````

From the map, the state of North Carolina is the largest state which imported meat/seafood into the state of Virginia by truck if not considering the state of Virginia itself.